Molecular dynamics simulation of synchronization in driven particles

### 2021-01-06 manuscript/manuscript_ajp_2020.tex
finished Ex. 2

Newton's second law for an individual particle
$m \vec{a}_i = \sum \vec{F}$ is simplified
by the assumption $\vec{a}_i$ is zero in overdamped model.
%Newton's second law can be rearranged %for the velocity
%to
The equation of motion for an isolated particle is
%solved for velocity 
\begin{equation}
  \eta \vec{v}_i = \vec{F}^l_{i} + \vec{F}^{D}(t).
    \label{eq:motion}
\end{equation}
with the viscosity coefficient $\eta = 1$ in units,
which we describe in more detail in Exercise~\ref{ex:reynolds}.
In Section~\ref{sec:problems} Exercise~\ref{ex:n2l}
we invite the reader to confirm this result.

@@

The slope of $y/\lambda$
is proportional to the net force on the particle (See Eq.~\ref{eq:motion}).
This can be seen in 
Fig.~\ref{fig:0} %we demonstrate this relationship,
where local extrema appear in $y/\lambda$
when $F_{D}(t) \approx 0 $ and 
When $F^D(t) > A_p$, a particle can 
overcome the barrier height of the landscape maxima,
and 
the particle hops between minima in the energy landscape.
In this example
we note 
the particle moves
in the positive y-direction
through $\Delta y = 2 \lambda$ in one time period $\Delta t = T$.
When $F_{D}(t) < 0 $
the particle moves in the negative y-direction 
for a short time.
%reaching a minimum position
%of $y/\lambda = 1$
%over the total period $T = 100$.
The average velocity $\bar{v}_y$
is the average displacement $\Delta y = y(t_0+T) - y(t_0)$
over the period of the driving force.
%In Fig. ~\ref{fig:0}
%the average displacement during one time period is a single wavelength
%of the substrate $y(t_0+T) - y(t_0) = \lambda$.
Thus the average velocity 
is $\bar{v}_y = 2 \lambda f$ where $T = 1/f$.

@@

\item Newton's second law states that the sum of forces on a particle is proportional to the acceleration of the particle.
  \begin{equation}
  m \vec{a}_i = \sum \vec{F}
  \label{eq:n2l}
  \end{equation}
  Demonstrate that Eq.~\ref{eq:motion} is obtained from Newton's second law.
  \label{ex:n2l}

>>>>

Newton's second law for an individual particle
$m \vec{a}_i = \sum \vec{F}$ is simplified
by the assumption $\vec{a}_i$ is zero in overdamped model.
%Newton's second law can be rearranged %for the velocity
%to
The equation of motion for an isolated particle is
%solved for velocity 
\begin{equation}
  \eta \vec{v}_i = \vec{F}^l_{i} + \vec{F}^{D}(t).
    \label{eq:motion}
\end{equation}
with the viscosity coefficient $\eta = 1$,
which we describe in more detail in Table~\ref{tab:1}
and Exercise~\ref{ex:reynolds}.
In Section~\ref{sec:problems} Exercise~\ref{ex:n2l}
we invite the reader to confirm this result.

@@

The slope of $y/\lambda$
is proportional to the net force on the particle (See Eq.~\ref{eq:motion}).
This can be seen in 
Fig.~\ref{fig:0} %we demonstrate this relationship,
where local extrema appear in $y/\lambda$
when $F_{D}(t) \approx 0 $. 
When $F^D(t) > A_p$, a particle can 
overcome the barrier height of the landscape maxima,
and 
the particle hops between minima in the energy landscape.
In this example
we note 
the particle moves
in the positive y-direction
through $\Delta y = 2 \lambda$ in one time period $\Delta t = T$.
When $F_{D}(t) < 0 $
the particle moves in the negative y-direction 
for a short time.
%reaching a minimum position
%of $y/\lambda = 1$
%over the total period $T = 100$.
The average velocity $\bar{v}_y$
is the average displacement $\Delta y = y(t_0+T) - y(t_0)$
over the period of the driving force.
%In Fig. ~\ref{fig:0}
%the average displacement during one time period is a single wavelength
%of the substrate $y(t_0+T) - y(t_0) = \lambda$.
Thus the average velocity 
is $\bar{v}_y = 2 \lambda f$ where $T = 1/f$.

@@

\item Newton's second law states that
  the acceleration of a particle $i$
  is proportional to 
  the sum of forces on a particle 
  \begin{equation}
  m_i \vec{a}_i = \sum \vec{F}_i
  \label{eq:n2l}
  \end{equation}
  where the constant of proportionality is the
  inertial mass $m_i$
  The addition of a dissipative force in a dynamical model
  on a colloid is typically modeled
  with a drag force proportional to the particle's velocity
  in the opposite direction of motion 
  $\vec{F}^{drag} = - \eta \vec{v}_i$
  where $\eta$ is the drag coefficient.
  Demonstrate
  the ratio of $m/\eta$ has units of time, 
  %This ratio of the acceleration coefficient $m$
  %to the drag coefficient $\eta$
  %is
  known as the momentum relaxation time.
  The momentum relaxation time is 
  known to be small for
  particles with low Reynolds numbers,
  indivating 
  a regime in which the acceleration term can be ignored
  entirely.
  Demonstrate that a particle confined to a landscape exerting force
  $F^l(\vec{r}_i)$ subject to a time dependent drive $F^D(t)$
  can be modeled with the equation of motion described in 
  Eq.~\ref{eq:motion}. 
  \label{ex:n2l}
